\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-12-03 main.tex
Updates from Overleaf

\author[PHYS,SIMES]{Logan Bishop-Van Horn}\ead{lbvh@stanford.edu}
\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
\end{equation}
where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).

@@

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh. Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        -\mathbf{K}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,k}\mathbf{h}_{z,\,\mathrm{eff},\,k}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,k}
            & \text{inside hole }k\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

@@

\begin{table*}
\centering
\begin{tabular}{|l|l|l|}
\hline
\SuperScreen                             & Set-theoretic  & Boolean   \\ \hline \hline
\inline{polygonA.union(polygonB)}        & $A\cup B$      & \inline{OR}      \\
\inline{polygonA.intersection(polygonB)} & $A\cap B$      & \inline{AND}     \\
\inline{polygonA.difference(polygonB)}   & $A\setminus B$ & \inline{AND NOT} \\
\inline{polygonA.difference(polygonB, symmetric=True)} & $(A\setminus B)\cup(B\setminus A)$ & \inline{XOR} \\ \hline
\end{tabular}
\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations. The vertices of \inline{polygonA} lie in set $A$ and the vertices of \inline{polygonB} lie in the set $B$. The object \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package.}
\label{table:polygon}
\end{table*}

@@

Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them. Films and holes are represented by instances of the \inline{superscreen.Polygon} class. All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
% A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
\inline{Polygons} can constructed and combined using set-theoretic operations. Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$. Note that \inline{polygonB} can be another \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or one of several compatible types of objects from the \inline{shapely} package.

In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region. The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles). In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become. The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is performed, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

@@

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$. (a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. (b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. (c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. (d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:ring-with-slit}
\end{figure*}

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/fluxoid.pdf}
    \caption{(a) Magnetic field and (b) current density distributions generated by Code Block~\ref{code:fluxoid} for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The film is subject to a uniform applied out-of-plane field of 1 mT, and both holes are set to be in the $n=0$ fluxoid (i.e. Meissner) state. The resulting ciruclating currents are $I_\text{rectangle} = -1.071$ mA and $I_\text{ellipse} = -1.589$ mA, and the residual fluxoid for each hole is smaller than $10^{-7}\,\Phi_0$. These results were computed using a mesh with approximately 5,000 vertices and 10,000 triangles.}
    \label{fig:fluxoid}
\end{figure}

@@

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()}. A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e). Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid. See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

@@

\begin{figure*}[h!]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated using \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$. (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film. The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis. (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c). In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (f) Error in the total simulated fluxoid relative to $\Phi_0$: error = $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure*}

@@

As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
\begin{equation}
    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
\end{equation}
where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$. The mutual inductance values for a set of holes form a mutual inductance matrix. The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem. If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_{S_i}$, the flux through hole $i$. For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method. For example, the mutual inductance matrix for the device shown in Figure~\ref{fig:fluxoid} is:
\begin{equation*}
    \mathbf{M} = 
    \begin{pmatrix}
    	10.319 & -1.536 \\
        -1.527 & 7.130
    \end{pmatrix}
    \,\mathrm{pH},
\end{equation*}
where the matrix is indexed as $$\begin{pmatrix}\text{ellipse}\\\text{rectangle}\end{pmatrix},$$
and the ``fractional asymmetry'' of $\mathbf{M}$ is $|M_{01} - M_{10}| / \min(|M_{01}|, |M_{10}|)\approx 0.6\%$.

>>>>

\author[PHYS,SIMES]{Logan Bishop-Van Horn}\ead{lbvh@stanford.edu}
\author[PHYS,AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}

@@

A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}. In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$. The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to
\begin{equation}
    \label{eq:london}
    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
\end{equation}
where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).

@@

\subsection{Vortices}
\label{section:model:vortices}
In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices. The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
\begin{align}
\begin{split}
    \label{eq:applied_to_stream_vortices}
    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
    = \\
    &-\int_F\left[
        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
    ]g(\pvec{r}')\,\mathrm{d}^2r',
\end{split}
\end{align}
where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge). By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices. For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$. The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.

@@

The matrix version of Eq.~\ref{eq:Heff_sub} is
\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh. Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        -\mathbf{K}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,h}\mathbf{h}_{z,\,\mathrm{eff},\,h}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,h}
            & \text{inside hole }h\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

@@

\begin{table*}
\centering
\begin{tabular}{|l|l|l|}
\hline
\SuperScreen                             & Set-theoretic  & Boolean   \\ \hline \hline
\inline{polygonA.union(polygonB)}        & $A\cup B$      & \inline{OR}      \\
\inline{polygonA.intersection(polygonB)} & $A\cap B$      & \inline{AND}     \\
\inline{polygonA.difference(polygonB)}   & $A\setminus B$ & \inline{AND NOT} \\
\inline{polygonA.difference(polygonB, symmetric=True)} & $(A\setminus B)\cup(B\setminus A)$ & \inline{XOR} \\ \hline
\end{tabular}
\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations.}
\label{table:polygon}
\end{table*}

@@

Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them. Films and holes are represented by instances of the \inline{superscreen.Polygon} class. All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
% A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
\inline{Polygons} can constructed and combined using set-theoretic operations. Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$. Note that \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package~\cite{shapely}.

In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that do not necessarily correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region. The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles). In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become. The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is performed, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}({\bf a}) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

@@

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$. ({\bf a}) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. ({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:ring-with-slit}
\end{figure*}

@@

While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values. For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value. This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function. For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}. For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters. Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}. It is important to note that while \SuperScreen can calculate the field and current distributions or a given fluxoid state, the model does not capture transitions between fluxoid states.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{examples/images/fluxoid.pdf}
    \caption{({\bf a}) Magnetic field and ({\bf b}) current density distributions generated by Code Block~\ref{code:fluxoid} for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole. The film is subject to a uniform applied out-of-plane field of 1 mT, and both holes are set to be in the $n=0$ fluxoid (i.e. Meissner) state. The resulting ciruclating currents are $I_\text{rectangle} = -1.071$ mA and $I_\text{ellipse} = -1.589$ mA, and the residual fluxoid for each hole is smaller than $10^{-7}\,\Phi_0$. These results were computed using a mesh with approximately 5,000 vertices and 10,000 triangles.}
    \label{fig:fluxoid}
\end{figure}

@@

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()}. A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e). Figure~\ref{fig:pearl}({\bf e}) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid. See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

@@

\begin{figure*}[h!]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated using \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$. ({\bf a}) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film. The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis. ({\bf b}) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in ({\bf a}). ({\bf c}) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). ({\bf d}) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in ({\bf c}). In ({\bf a}) and ({\bf c}), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. ({\bf e}) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. ({\bf f}) Error in the total simulated fluxoid relative to $\Phi_0$: error = $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure*}

@@

As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
\begin{equation}
    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
\end{equation}
where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$. The mutual inductance values for a set of holes form a mutual inductance matrix. The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem. In this context, the flux and supercurrent parts of the fluxoid correspond to the geometric and kinetic inductance respectively~\cite{Brandt2004-ew}. If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film, the fluxoid $\Phi^f_{S_i}$ is equal to the flux through hole $i$, and the total inductance is equal to the geometric inductance. For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method. For example, the mutual inductance matrix for the device shown in Figure~\ref{fig:fluxoid} is:
\begin{equation*}
    \mathbf{M} = 
    \begin{pmatrix}
    	10.319 & -1.536 \\
        -1.527 & 7.130
    \end{pmatrix}
    \,\mathrm{pH},
\end{equation*}
where the matrix is indexed as $$\begin{pmatrix}\text{ellipse}\\\text{rectangle}\end{pmatrix},$$
and the ``fractional asymmetry'' of $\mathbf{M}$ is $|M_{01} - M_{10}| / \min(|M_{01}|, |M_{10}|)\approx 0.6\%$.
